paper_replication

### 2021-12-15 paper_replication.Rmd
Resize plot

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#calculate propensity scores
propensitywts <- glm(inanalysis ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008, data=countydem, family=binomial())
# summary(propensitywts)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=5, fig.align='center'}
#calculate propensity scores
propensitywts <- glm(inanalysis ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008, data=countydem, family=binomial())
# summary(propensitywts)
